### 2019-05-20 VM552/HW1/submission.tex
Hw1 done

\title{	
\normalfont \normalsize 
\textsc{Shanghai Jiao Tong University, UM-SJTU JOINT INSTITUTE} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Methods of Applied Mathematics I\\ HW3 \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Yu Cang \\ 018370210001} % Your name

@@

\section{Exercise3.1}
	\begin{proof}
		Let $\phi(x) = (x^2 - 1)^n$, then
		\begin{equation}
			\phi(\pm 1) = \phi^{(1)}(\pm 1) = \cdots = \phi^{(n-1)}(\pm 1) = 0
		\end{equation}
		The $L^2$ norm of $P_n(x)$ is
		\begin{equation}
			\begin{aligned}
				||P_n||_2  & = \sqrt{\int_{-1}^{1} P_n^2(x) dx}\\
						   & = \sqrt{(\frac{1}{2^n n!})^2 \int_{-1}^{1} [\phi^{(n)}(x)]^2 dx}\\
						   & = \sqrt{(\frac{1}{2^n n!})^2 (-1)^n \int_{-1}^{1} \phi^{(2n)}(x) \phi(x) dx} \quad \text{(Integrate by parts)}\\
						   & = \sqrt{(\frac{1}{2^n n!})^2 (-1)^n (2n)! \int_{-1}^{1} (x^2 - 1)^n dx}\\
						   & = \sqrt{(\frac{1}{2^n n!})^2 (-1)^n (2n)! \cdot 2 \int_{0}^{\frac{\pi}{2}} (sin^2(x) - 1)^n cos(x) dx}\\
						   & = \sqrt{(\frac{1}{2^n n!})^2 (2n)! \cdot 2 \int_{0}^{\frac{\pi}{2}} cos^{2n+1}(x) dx}\\
			\end{aligned}
		\end{equation}
		Since
		\begin{equation}
			\int_{0}^{\frac{\pi}{2}} cos^{2n+1}(x) dx = \frac{2 \times 4 \times \cdots \times (2n)}{1\times3\times \cdots \times (2n+1)} 
		\end{equation}
		substitute it into the norm equation of $P_n$ yields
		\begin{equation}
			||P_n||_2 = \sqrt{(\frac{1}{2^n n!})^2 (2n)! \cdot 2 \cdot \frac{2 \times 4 \times \cdots \times (2n)}{1\times3\times \cdots \times(2n+1)}} = \sqrt{\frac{2}{2n+1}}
		\end{equation}
	\end{proof}

\section{Exercise3.2}
	\begin{enumerate}
		\item 
			Consider the projection of $f(x)$ onto $P_0(x)$, $P_1(x)$ and $P_2(x)$ correspondingly
			\begin{equation}
				(f, P_0) = \int_{-1}^{1} e^x dx = e - \frac{1}{e}
			\end{equation}

			\begin{equation}
				(f, P_1) = \int_{-1}^{1} x e^x dx = \frac{2}{e}
			\end{equation}

			\begin{equation}
				(f, P_2) = \int_{-1}^{1} \frac{3x^2 -1}{2} e^x dx = e - \frac{7}{e}
			\end{equation}
			As $(P_i, P_j)=0$ when $i \neq j$, $p(x)$ can be written as linear combination of $P_i$
			\begin{equation}
				p(x) = a_0 P_0(x) + a_1 P_1(x) + a_2 P_2(x)
			\end{equation}
			with coefficient $a_i$ given as
			\begin{equation}
				a_i = \frac{(f, P_i)}{(P_i, P_i)} = \frac{2i+1}{2} (f, P_i)
			\end{equation}
			Finally
			\begin{equation}
				p(x) = 1.1752 P_0(x) + 1.1036 P_1(x) + 0.3578 P_2(x)
			\end{equation}

		\item 
		The plot(Fig \ref{fig:comp}) is provided for comparsion.

		\begin{figure}[!htbp]
			\centering
			\includegraphics[]{ApproximationCompare.png}
			\caption{Comparsion of different approximation for $e^x$}
			\label{fig:comp}
		\end{figure}

		The distinction is quite obvious and Legendre polynomials does better than taylor series expansion at zero point.

@@

\section{Exercise3.3}
	\begin{enumerate}
		\item

		\item

>>>>

\title{	
\normalfont \normalsize 
\textsc{Shanghai Jiao Tong University, UM-SJTU JOINT INSTITUTE} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Mechatronic Systems Design\\ HW1 \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Yu Cang \quad 018370210001} % Your name

@@

The autonomous drone is a new type of mechatronic system gaining popularity nowadays. 
\section{Hardware}
	Generally, it is based on the traditional multi-rotor configuration like Fig(\ref{fig:drone}), where 4 or 6 rotors are placed symmetrically around the central body. The central body contains power supply packages, controling unit and sensing facilities, with carbon fiber shell protecting them away from external dust, moist, or possible damage.

	\begin{figure}[!h]
		\centering
		\includegraphics[width=5cm]{pic/drone.jpg}
		\caption{Autonomous drone}
		\label{fig:drone}
	\end{figure}

	Usually, a camera is mounted at the bottom for taking pictures or performing vision-based guiding.
	For professional use, both laser radar and milimeter-wave radar are equipped for advanced perception.

\section{Components}
	The most important 3 components are
	\begin{enumerate}
		\item \textbf{Sensing Unit}\\
			Usually, it is composed of accelerometer, gyroscope, barometer, geomagnetic sensor and GPS.These sensors are usually in chip format called MEMS, and can be mounted on the surface of PCB precisely, see Fig(\ref{fig:imu_pcb}).\\

			\begin{figure}[!h]
				\centering
				\includegraphics[width=5cm]{pic/imu.png}
				\caption{Sensing Unit PCB}
				\label{fig:imu_pcb}
			\end{figure}

			\begin{enumerate}
				\item \textit{Accelerometer}\\
					It provides the inertial force info, and 3-axis pose(Roll Yaw, Pitch) can be estimated from acceleration in each axis.
				\item \textit{Gyroscope}\\
					It provides the angular velocity info. It is based on the conservation of angular momentum.
				\item \textit{Barometer}\\
					It provide the pressure of atomosphere, and height can be estimated.
				\item \textit{Geomagnetic sensor}\\
					Guiding the \textbf{North} direction.
				\item \textit{GPS}\\
					Global position like longtitude and latitude are provided. Timing is also available.
			\end{enumerate}

			In general, sensing unit provides the state of drone.

		\item \textbf{Perception Facility}\\
			To provide the infomation of environment, Radar, optical flow and ultrasonic sensor are integrated.

			\begin{enumerate}
				\item \textit{Laser Radar}\\
					Usually in shape like Fig(\ref{fig:lidar}), for sensing obstacles around. It can also be done using an RGB-D camera.
				\item \textit{Milimeter-wave Radar}\\
					Barometer may not accurate, Radar has better resolution on determining height.
				\item \textit{Optical Flow}\\
					Local positioning and velocity estimation.
				\item \textit{Ultrasonic sensor}\\
					Sensing in a specific direction, it has similar function as LiDAR but shorter range.
			\end{enumerate}

			\begin{figure}[!htbp]
				\centering
				\begin{minipage}[t]{0.48\textwidth}
					\centering
					\includegraphics[width=5cm]{pic/lidar.png}
					\caption{LiDAR}
					\label{fig:lidar}
				\end{minipage}
				\begin{minipage}[t]{0.48\textwidth}
					\centering
					\includegraphics[width=5cm]{pic/radar.jpg}
					\caption{Milimeter-wave Radar}
					\label{fig:mm-wave}
				\end{minipage}
			\end{figure}

		\item \textbf{Control Unit}\\
			It do realtime response under both internal and external constraints. Signals in PWM form are generated to the electrical speed regulator to drive the motors. Usually, serial PID algorithm is used.

@@

\section{Specifications}
	Usually, this kind of automous drones can be used for agricultural, topographic or transportation purpose. Typically, the diameter ranges from 0.5 to 2m, and weighs 2 to 20kg.\\
	Due to the energy density limit of lithium battery, endurance is usually about 20 minutes.\\
	For safety issues, flight speed is usually lower than 5m/s, and flight height is restricted to 10m.

\section{Challenges in design and control}
	\begin{enumerate}
		\item 
			Data fusion.
		\item 
			Proper placement to minimize vibration.
		\item 
			PID param tuning.
		\item 
			Obstacle detection.
		\item 
			Reliable wireless communication.
	\end{enumerate}

\section{Future trends of developments}
	\begin{enumerate}
		\item 
			Communication for long range and high fidelity.
		\item 
			Advanced and robust control algorithm.
		\item 
			Optimized aerodynamic shape design(For agricultural spray).
		\item 
			Higher energy density batteries or use gasoline.
		\item 
			More mature environment perception.
	\end{enumerate}
